Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
adding sm bug in discussion

>>>>

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \smonkey\ development team as a
bug, the bug was confirmed in a few hours.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    "use strict"
    010
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
  \vspace{-1ex}
\end{figure}

This is a test case original from the \hermes suite using test transplantation.
According the specification, in strict mode, the engine must use 
the prefix '0o' or '0O' to represents octal numeric literals. It was an
issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
The others engine throws a SyntaxError due the missing of the octal token, but 
\smonkey returns a integer 8 that represents 010 in octal literal.
